Twisted \(M\)-theory and its perturbative quantization.

### 2021-02-17 paper.tex
overhaul section 1

One of the fundamental geometric objects will be the sheaf of divergence-free holomorphic vector fields on $X$. 
We will utilize a convenient semi-free resolution of this sheaf in the category of $C^\infty$-modules.

If $j$ is an integer, we let $\Omega^{0,j}(X, V)$ denote the space of Dolbeault forms of type $j$ on with values in $V$.
The $\dbar$ operator for $V$ is of the form $\dbar : \Omega^{0,j}(X, V)\to \Omega^{0,j+1}(X)$.
This operator defines the Dolbeault complex of $V$
\[
  \Omega^{0,\bu}(X, V) = \left(\Omega^{0,j}(X, V)[-j] \; , \; \dbar\right)
\]
which is a free resolution for the sheaf of holomorphic sections of $V$.
Applying this to the holomorphic tangent bundle $V = \T_X$, we obtain a resolution of the sheaf of holomorphic vector fields.

@@

Now, suppose $X$ is a Calabi--Yau manifold with holomorphic volume form $\Omega$.
The holomorphic divergence operator extends to the Dolbeault complex to take the form
\[
  \partial_\Omega : \Omega^{0,\bu}(X, \T_X) \to \Omega^{0,\bu}(X)
\]
and is defined by the formula
\[
  \partial_\Omega (\mu) \wedge \Omega = L_\mu (\Omega)
\]
where, on the right hand side, we mean the Lie derivative of $\Omega$ with respect to $\mu$.

Using the divergence operator, we define the double complex of sheaves
\[
\Omega^{0,\bu}(X, \T_X) \xto{\partial_\Omega} \Omega^{0,\bu}(X) [-1] 
\]
where the horizontal differential is the divergence operator and the vertical differential is the $\dbar$ operator (which we have left implicit). 
We denote the totalization of this double complex of sheaves $\cS$.

It is immediate to check that $\cS$ provides a free resolution of the sheaf of holomorphic divergence-free vector fields on $X$.
Furthermore, there is a natural Lie bracket on $\cS$ given by the Schouten--Nijenhous bracket $\{-,-\}_{\rm NS}$ which is compatible with the usual Lie bracket of holomorphic vector fields. 
In other words, $\cS$ is a sheaf of dg Lie algebras and the inclusion of holomorphic divergence-free vector fields is a quasi-isomorphism of sheaves of Lie algebras.

@@

The space of differential forms on any smooth manifold $L$ is a commutative dg algebra $\Omega^{\bu}(L) = \left(\oplus_{k}\Omega^{k}(L)[-k], \d_{\dR}\right)$.
By taking the tensor product with the dg Lie algebra $\cS(X)$ we obtain the dg Lie algebra
\beqn\label{localLie}
  \cS(X) \; \Hat{\otimes} \; \Omega^{\bu}(L)
\eeqn
where $X$ is a Calabi--Yau manifold and $L$ is a smooth manifold.
The differential in this dg Lie algebra is of the form $\dbar \otimes 1 + \partial_\Omega \otimes 1 + 1 \otimes \d_{\rm dR}$, which we will abbreviate by $\dbar + \partial_\Omega + \d_{\rm dR}$.
The bracket is defined using the bracket on $\cS(X)$ together with the wedge product of forms on $\Omega^\bu(L)$ by the formula
\[
  [\mu \otimes \alpha, \nu \otimes \beta] = \{\mu, \nu\}_{\rm NS} \otimes (\alpha \wedge \beta) .
\]

We remark that the structure maps of this Lie algebra, namely the differential and bracket, are given by differential and bidifferential operators, respectively.
In this sense, it fits the definition of a {\em local dg Lie algebra} on the product manifold $X \times L$, see Definition ?? \ref{CG2}.

Associated to any local dg Lie algebra is a classical field theory in the BV formalism that one refers to as ``$BF$-theory'' and it is defined as follows.
Denote the sheaf of sections of the local dg Lie algebra by $\cL$.
The fields of the associated BV theory are pairs
\[
  (A, B) \in \cL[1] \oplus \cL^{!}[-2]
\]
and the action functional reads $\int B F_{A} = \int B (\d_{\cL}A + \frac12 [A,A])$.
Here $\d_{\cL}$ denotes the differential on $\cL$ and $[\cdot,\cdot]$ is the Lie bracket.
Notice that the equations of motion for the $A$-field is simply the Maurer--Cartan equation $\d_\cL A + \frac12 [A,A] = 0$.
For the $B$-field the equations of motion read $\d_\cL B + [A, B] = 0$.

For the case at hand, we consider the $BF$ theory associated to the local dg Lie algebra  $\cS(X) \otimes \Omega^\bu(L)$ defined on the product $X \times L$ where $X$ is a Calabi--Yau manifold and $L$ is a smooth manifold.
Denote by $d \in \ZZ$ the sum $\dim_{\CC}(X) + \dim_{\RR}(L)$.

The fields decompose as
\[
(\mu, \gamma) = (\mu^1 + \mu^0, \gamma^0 + \gamma^1)
\]
where
\[
  \begin{array}{ccl}
    \mu = \mu^1+\mu^0 & \in & \left(\Omega^{0,\bu}(X, \T_X)[1] \oplus \Omega^{0,\bu}(X) \right) \; \Hat{\otimes} \; \Omega^{\bu}(L) \\
    \gamma = \gamma^0 + \gamma^1 & \in & \left(\Omega^{0,\bu}(X)[-1] \oplus \Omega^{1,\bu}(X)[-2] \right) \; \Hat{\otimes}\; \Omega^{\bu}(L)[d] .
  \end{array}
\]
Notice that what we called the ``$A$''-field in the general definition of $BF$ theory we are now calling $\mu$ and what we called the ``$B$''-field we are now calling $\gamma$.
The action of this version of $BF$ theory simply reads 
\[
\int_{X \times L} \left[\gamma \vee \left(\dbar \mu + \partial_\Omega \mu + \d_{\dR} \mu + \frac12 [\mu, \mu] \right) \right] \wedge \Omega .
\]
This theory is defined on any geometry $X \times L$ where $X$ is a Calabi--Yau manifold and $L$ is a one-dimensional smooth manifold.
There is a deformation of this theory that we will be most concerned with.

%By force of habit, we will still refer to the theory with these particular fields as $BF$-theory.
%Notice that while the definition of $\mu$  of the dimension, the field $\gamma$

@@

\subsubsection{Chern--Simons deformation}
The theory we have just described admits a deformation by a higher Chern--Simons term.
We explain how this relates to the familiar Chern--Simons term in eleven-dimensional supergravity in Section \ref{sec:evidence}.

We will be mostly interested in the case that $X$ is a Calabi--Yau five-fold and $L$ is a real one-dimensional manifold.
In the notation of the last section, $d = 6$, so the field $\gamma$ takes the form
\[
  \gamma \in \left(\Omega^{0,\bu}(X)[6] \oplus \Omega^{1,\bu}(X)[5] \right) \otimes \Omega^\bu(L).
\]

What is important for us is not simply BF theory for the dg Lie algebra $\cS(X) \otimes \Omega^\bu(L)$, but a certain deformation of it.
We consider a theory whose fields are that of the BF theory but whose action functional is of the form $S_{\rm BF} + J$, where $J$ is a local functional that purely depends on the fields $\gamma$.
It is defined by the following formula
\[
J(\gamma) = \frac16 \int_{X\times L} \gamma \partial \gamma \partial \gamma .
\]

First off, we notice an inconsistency in the cohomological degrees of the functionals $S_{\rm BF}$ and $J$.
Being a classical action functional $S_{\rm BF}$ is, of course, ghost degree zero.
However, we observe that $J$ is of ghost degree $+6$.
In order to make sense of the deformed theory, therefore, we must consider the space of fields as a $\ZZ/2$-graded object rather than a $\ZZ$-graded one.

So, in order to make sense of the action functional $S_{\rm BF} + J$ as a homogenously even functional, the $\ZZ /2$-graded space of fields takes the form
\[
  \begin{array}{ccl}
    \mu = \mu^1+\mu^0 & \in & \left(\pv^{1,\bu}(X)[1] \oplus \pv^{0,\bu}(X) \right) \; \Hat{\otimes} \; \Omega^{\bu}(L) \\
    \gamma = \gamma^0+ \gamma^1 & \in & \left(\Omega^{0,\bu}(X)[1] \oplus \Omega^{1,\bu}(X) \right) \; \Hat{\otimes}\; \Omega^{\bu}(L) .
  \end{array}
\]
Here, we have used the following convention for $\ZZ/2$-graded complexes.
If $V$ is a $\ZZ/2$-graded vector space with even part $V^0$ and odd part $V^1$, then $V[1]$ is a $\ZZ/2$-graded vector space with even part $V^1$ and odd part $V^0$.

With the issue of gradings out of the way, we turn to the question of whether this is a well-defined classical BV theory.
In order for this to be true, we must see that the total action functional $S_{\rm BF} + J$ satisfies the classical master equation
\[
  \{S_{\rm BF} + J , S_{\rm BF} + J\} = 0 .
\]
Of course, we know the undeformed BF-theory satisfies the classical master equation $\{S_{\rm BF}, S_{\rm BF}\} = 0$.
Additionally, since $\gamma$ does not pair with itself under the antibracket, we also see that $\{J,J\}=0$.
What remains is to see that $J$ is closed for the differential $\{S_{\rm BF}, \cdot\}$.

\begin{lem}
The functional $J = \frac16\int \gamma \partial \gamma \partial \gamma$ is closed for the differential $\{S_{\rm BF},\cdot\}$.
In particular, $S_{\rm BF} + J$ is a well-defined classical BV action.
\end{lem}

\begin{proof}
It is clear that $J$ is closed for the part of the differential arising from the kinetic term $\{S_{\rm free},\cdot\}$.
It remains to see that\brian{finish}
\end{proof}

\begin{rmk}
  We have actually shown something slightly stronger here.
  Namely, for any constant $c$ the functional $S_{\rm BF} + c J$ satisfies the classical master equation.
  This dependence on a coupling constant will be important later on in this paper.
\end{rmk}

\begin{dfn}\label{dfn:11dtheory}
Let $X$ be a Calabi--Yau five-fold and $L$ a one-dimensional smooth manifold.
Define the $\ZZ/2$-graded BV theory $\cT_{X \times L}$ (or simply just $\cT$) on
\[
  X \times L
\]
to be the deformation of BF theory for the $\ZZ/2$-graded local Lie algebra $\cS(X) \Hat{\otimes} \Omega^{\bu}(L)$ by the local functional $J (\gamma) = \frac16 \int_{X \times L} \gamma \partial \gamma \partial \gamma.$
\end{dfn}

%Unpacking this a bit, we see that the BV action functional for the theory $\cT$ splits as a sum
%\begin{equation}\label{11daction}
%  S_{\rm BF} + J
%\end{equation}
%where $J$ is as in the definition above and $S_{BF}$ is the action functional for the underlying BF theory which takes the form
%\[
%  S_{\rm BF} = \int \gamma \vdash \left(\dbar + \d_{\rm dR} + \partial_{\Omega}\right) \mu \wedge \Omega + \frac12 \int \gamma \vdash \{\mu,\mu\}_{\rm NS} \wedge \Omega .
%\]
%We will furthermore decompose $S_{\rm BF} = S_{\rm free}+I_{\rm BF}$ into its free and interacting pieces.

>>>>

Let $V$ be a holomorphic vector bundle. 
If $j$ is an integer, we let $\Omega^{0,j}(X, V)$ denote the space of anti-holomorphic Dolbeault forms of type $j$ on with values in $V$.
The $\dbar$ operator for $V$ is of the form $\dbar : \Omega^{0,j}(X, V)\to \Omega^{0,j+1}(X)$.
This operator is used to define the Dolbeault complex of $V$
\[
  \Omega^{0,\bu}(X, V) = \left(\Omega^{0,j}(X, V)[-j] \; , \; \dbar\right)
\]
which is a free resolution for the sheaf of holomorphic sections of $V$.
Applying this to the $k$th exterior power of the holomorphic tangent bundle $V = \wedge^k \T_X$, we obtain a resolution of the sheaf of $k$-linear polyvector fields which we denote by $\PV^{k,\bu} (X) = \Omega^{0,\bu}(X, \wedge^k \T_X)$.

Now, suppose $X$ is a Calabi--Yau manifold with holomorphic volume form $\Omega$.
The holomorphic divergence operator extends to the Dolbeault complex to take the form
\[
  \partial_\Omega : \PV^{1,\bu}(X) \to \PV^{0,\bu}(X)
\]
and is defined by the formula
\[
  \partial_\Omega (\mu) \wedge \Omega = L_\mu (\Omega)
\]
where, on the right hand side, we mean the Lie derivative of $\Omega$ with respect to $\mu$.

\begin{dfn} \label{dfn:classical}
Let $X$ be a Calabi--Yau five-fold and $L$ a smooth one-dimensional manifold.
{\em Eleven-dimensional twisted supergravity} on $X \times L$ is the $\ZZ/2$-graded BV theory on $X$ whose fields are pairs
\begin{align*}
\mu & \in \bigg(\Pi \PV^{1,\bu}(X) \oplus \PV^{0,\bu}(X) \bigg) \; \Hat{\otimes} \; \Omega^{\bu}(L) \\
\gamma & \in \bigg(\Pi \Omega^{0,\bu}(X) \oplus \Omega^{1,\bu} (X) \bigg) \; \Hat{\otimes} \; \Omega^{\bu}(L) 
\end{align*}
The BV pairing is $\int (\gamma \vee \mu) \wedge \Omega$ and the BV action is
\begin{equation}\label{eqn:bvaction}
S = \int_{X \times L} \left[\gamma \vee \left(\dbar \mu + \partial_\Omega \mu + \d_{\dR} \mu\right) \right] \wedge \Omega +  \frac12 \int_{X \times L} \left(\gamma \vee [\mu, \mu] \right) \wedge \Omega  + \frac16 \int_{X \times L} (1+\mu) \gamma \partial \gamma \partial \gamma .
\end{equation}
\end{dfn}

\begin{prop} \label{prop:cme}
The action functional $S$ satisfies the classical master equation~
\[
\{S, S\}=0.
\] 
\end{prop}

\subsubsection{Divergence-free vector fields}

Suppose that $X$ is a Calabi--Yau manifold of any dimension. 
One of the fundamental geometric objects in this paper will be the sheaf of divergence-free holomorphic vector fields on $X$. 
We will utilize a convenient semi-free resolution of this sheaf in the category of $C^\infty$-modules.

@@

Using the divergence operator, we define the double complex of sheaves
\begin{equation}\label{eqn:div}
\PV^{1,\bu}(X) \xto{\partial_\Omega} \PV^{0,\bu}(X) [-1] 
\end{equation}
where the horizontal differential is the divergence operator and the vertical differential is the $\dbar$ operator (which we have left implicit). 
%We denote the totalization of this double complex of sheaves $\cS$.

It is immediate to check that the totalization of this double complex provides a free resolution of the sheaf of holomorphic divergence-free vector fields on $X$.
Furthermore, there is a natural Lie bracket on this complex given by the Schouten--Nijenhuis bracket $\{-,-\}_{\rm NS}$ which is compatible with the usual Lie bracket of holomorphic vector fields. 
In other words, the complex is a sheaf of dg Lie algebras and the inclusion of holomorphic divergence-free vector fields is a quasi-isomorphism of sheaves of Lie algebras.

@@

The space of differential forms on any smooth manifold $M$ is a commutative dg algebra $\Omega^{\bu}(M) = \left(\oplus_{k}\Omega^{k}(M)[-k], \d_{\dR}\right)$.
By taking the tensor product with the dg Lie algebra \eqref{eqn:div} we obtain the dg Lie algebra
\beqn\label{localLie}
  \cS \define \left(\PV^{1,\bu}(X) \xto{\partial_\Omega} \Omega^{0,\bu}(X) [-1] \right) \; \Hat{\otimes} \; \Omega^{\bu}(M) 
\eeqn
where $X$ is a Calabi--Yau manifold and $M$ is a smooth manifold.
According to the direct sum decomposition, we will write sections of $\cS$ as $\mu^1 +\mu^0$. 
The differential in this dg Lie algebra is of the form $\dbar \otimes 1 + \partial_\Omega \otimes 1 + 1 \otimes \d_{\rm dR}$, which we will abbreviate by $\dbar + \partial_\Omega + \d_{\rm dR}$.
The bracket is defined using the bracket $\{\cdot,\cdot\}_{\rm NS}$ of polyvector fields together with the wedge product of forms on $\Omega^\bu(M)$ by the formula
\[
  [\mu \otimes \alpha, \nu \otimes \beta] = \{\mu, \nu\}_{\rm NS} \otimes (\alpha \wedge \beta) .
\]

We remark that the structure maps of this Lie algebra, namely the differential and bracket, are given by differential and bidifferential operators, respectively.
In this sense, $\cS$ fits the definition of a {\em local dg Lie algebra} on the product manifold $X \times M$, see Definition \cite[??]{CG2}.

\begin{lem}
A (perturbative) classical field theory in the BV formalism consists of two pieces of data:
\begin{itemize}
\item A local dg Lie algebra $(\cL, \d, [\cdot, \cdot])$, where $\cL$ is the sheaf of sections of a $\ZZ$-graded vector bundle $L$.
\item An $\cL$-invariant fiberwise non-degenerate map of vector bundles of degree $(-3)$:
\[
\< \cdot , \cdot \> \colon L \otimes L \to {\rm Dens} [-3] 
\]
where ${\rm Dens}$ is the bundle of densities. 
\end{itemize}
\end{lem}

Using the pairing, one reads of the BV action of the theory as
\[
S(\phi) = \frac12 \int \<\phi, \d \phi\> + \frac16 \int \<\phi, [\phi,\phi]\> 
\]
where $\phi \in \cL[1]$. 
The $\cL$-invariance of the pairing together with the Jacobi identity for the dg Lie algebra $\cL$ implies that $S$ automatically satisfies the classical master equation $\{S,S\} = 0$. 
To prove Proposition \ref{prop:cme} we will exhibit the theory in Definition \ref{dfn:classical} in terms of a local dg Lie algebra.

This local dg Lie algebra is built from the local dg Lie algebra $\cS$ together with a certain module. 
Denote by $d \in \ZZ$ the sum $\dim_{\CC}(X) + \dim_{\RR}(M)$.
Define the following sheaf of cochain complexes
\[
\cM \define \left(\Omega^{0,\bu} (X)[1] \xto{\partial} \Omega^{1,\bu} (X) \right) \; \Hat{\otimes} \; \Omega^\bu(M)[d]  . 
\]
The reason for the cohomological shifts will be apparent momentarily. 
According the direct sum decomposition, we will write sections of $\cM$ as $\gamma^0 + \gamma^1$.

The sheaf $\cM$ has the structure of a module over $\cS$, defined by Lie derivative:
\begin{align*}
[\mu^1, \gamma^0 + \gamma^1] \define L_{\mu^1} (\gamma^0) + L_{\mu^1} (\gamma^1) .
\end{align*}
Strictly speaking, the Lie derivative uses just the component of $\mu^1$ and $\gamma^i$ along $X$.
Along the manifold $M$ we simply take the wedge product of forms.

We now form the semi-direct product dg Lie algebra
\begin{equation}\label{eqn:dglie}
\cS \ltimes \cM^! [-3] .
\end{equation}
Recall, that we are decomposing the sections as $(\mu , \gamma) = (\mu^1 + \mu^0 , \gamma^0 + \gamma^1)$. 
One immediately verifies that this semi-direct product has the structure of a local dg Lie algebra.
Additionally, there is a non-degenerate pairing defined using the holomorphic volume form $\Omega$ on $X$ by the formula
\[
(\mu^1 + \mu^0 , \gamma^0 + \gamma^1) = \int_{X \times M} (\mu^1 \vee \gamma^1)\wedge \Omega + \int_{X \times M} (\mu^0 \gamma^0) \Omega
\]
which one can readily check is graded antisymmetric of degree $(-3)$ due to our cohomological shifts in the definition of $\cM$.

The associated BV action functional is of the form
\begin{equation}\label{eqn:modbfaction}
S_{0} (\mu,\gamma) = \int_{X \times M} \left[\gamma \vee \left(\dbar \mu + \partial_\Omega \mu + \d_{\dR} \mu\right) \right] \wedge \Omega +  \frac12 \int_{X \times M} \left(\gamma \vee [\mu, \mu] \right) \wedge \Omega .
\end{equation}
The fact that this BV action functional satisfies the classical master equation 
\[
\{S_0, S_0\} = 0 .
\]
follows automatically from the axioms of the dg Lie algebra structure on \eqref{eqn:dglie}.

The action $S_0$ is not the same as the action in Definition \ref{dfn:classical}--they differ by the last term in Equation \eqref{eqn:bvaction}. 
Before moving on to this term, we mention a relationship of the BV theory described by $S_0$ to ``BF'' theory.
%defined on the product $X \times M$ where $X$ is a Calabi--Yau manifold and $M$ is a smooth manifold.

%The fields decompose as
%\[
%(\mu, \gamma) = (\mu^1 + \mu^0, \gamma^0 + \gamma^1)
%\]
%where
%\[
%  \begin{array}{ccl}
%    \mu = \mu^1+\mu^0 & \in & \left(\PV^{1,\bu}(X) [1] \oplus \Omega^{0,\bu}(X) \right) \; \Hat{\otimes} \; \Omega^{\bu}(L) \\
%    \gamma = \gamma^0 + \gamma^1 & \in & \left(\Omega^{0,\bu}(X)[-1] \oplus \Omega^{1,\bu}(X)[-2] \right) \; \Hat{\otimes}\; \Omega^{\bu}(L)[d] .
%  \end{array}
%\]
%Notice that what we called the ``$A$''-field in the general definition of BF theory we are now calling $\mu$ and what we called the ``$B$''-field we are now calling $\gamma$.
%The action of this modified version of BF theory reads 
%\[
%\Tilde{S}_{BF} (\mu,\gamma) = \int_{X \times M} \left[\gamma \vee \left(\dbar \mu + \partial_\Omega \mu + \d_{\dR} \mu + \frac12 [\mu, \mu] \right) \right] \wedge \Omega .
%\]
%This theory is defined on any geometry $X \times M$ where $X$ is a Calabi--Yau manifold and $M$ is a smooth manifold.
%We have used the tilde in the notation to indicate that we have made a small re-identification of the fields of BF theory in Equation \eqref{eqn:modified}. 
%There is a deformation of this theory that we will be most concerned with.

%By force of habit, we will still refer to the theory with these particular fields as BF-theory.
%Notice that while the definition of $\mu$  of the dimension, the field $\gamma$

@@

\subsubsection{Relationship to ``BF'' theory}

Associated to any local dg Lie algebra is a classical field theory in the BV formalism that one refers to as BF-theory and it is defined as follows.
Denote the local dg Lie algebra by $\cA$, it is the sheaf of sections of some $\ZZ$-graded vector bundle $A$. 
The fields of the associated BV theory are pairs
\[
  (A, B) \in \cA[1] \oplus \cA^{!}[-2] .
\]
Here $\cA^!$ denotes the sheaf of sections of the bundle $L^* \otimes {\rm Dens}$, where ${\rm Dens}$ is the bundle of densities. 
The action functional reads $S_{\rm BF} = \int B F_{A} = \int B (\d_{\cL}A + \frac12 [A,A])$.
In terms of the local Lie algebra description, the action is completely determined by the dg Lie algebra structure on $\cA \ltimes \cA^![-3]$. 
Here $\d_{\cA}$ denotes the differential on $\cA$ and $[\cdot,\cdot]$ is the Lie bracket.
Notice that the equations of motion for the $A$-field is simply the Maurer--Cartan equation $\d_\cA A + \frac12 [A,A] = 0$.
For the $B$-field the equations of motion read $\d_\cA B + [A, B] = 0$.

The theory described in the previous section is closely related to BF theory for the local Lie algebra $\cA = \cS$. 
Indeed, using the holomorphic volume form, one has an isomorphism of sheaves of cochain complexes
\begin{equation}\label{eqn:modified}
\Omega \colon \cM \xto{\cong} \cS^! .
\end{equation}
So, at the level of fields, $\Omega$ determines an isomorphism of cochain complexes
\begin{equation}\label{eqn:omega}
\Omega \colon \cS \oplus \cM [-3] \xto{\cong} \cS \oplus \cS^![-3]  .
\end{equation}
On the left-hand side is the underlying space of fields of the theory defined in the last section \eqref{eqn:modified}, and on the right-hand side is the underlying space of fields of BF theory for $\cA = \cS$. 
However, this identification is {\em not} a map of local dg Lie algebras.

Nevertheless, the BV theory described by $\cS \ltimes \cM [-3]$ and BF theory are equivalent. 
The point is that there is an $L_\infty$ morphism between the two underlying local dg Lie algebras, whose linear component agrees with the map \eqref{eqn:omega}.

\begin{prop}
There is an $L_\infty$ map of local Lie algebras
\[
\Phi \colon \cS \ltimes \cM[-3] \to \cS \ltimes \cS^! [-3]
\]
whose linear term $\Phi^{(1)}$ is an isomorphism of cochain complexes that preserves the local pairings.
In particular, the BV theory described by the action functional $S_0$ in \eqref{eqn:modbfaction} and BF theory for the local Lie algebra $\cS$ are equivalent. 
\end{prop}

\begin{proof} 
The $L_\infty$ map is the identity on $\cS$ and so arrises from a map of $\cS$-modules 
\[
\Phi \colon \cM [-3] \to \cS^![-3]
\]
that we denote by the same symbol.

One has
\[ 
\cS^! [-3] = \left(\Omega^{5, \bu}(X) \xto{\partial_\Omega^!} \Pi \Omega^{5,\bu} (X, \T^*_X) \right) \; \Hat{\otimes} \; \Omega^\bu(M) 
\]
\brian{fix shifts}
where $\partial_\Omega^!$ sends $f \Omega$ to $(\partial f) \otimes \Omega$ (and is the identity on $\Omega^\bu(M))$. 
The $\cS$-module structure is the one by which $\PV^{1,\bu}(X)$ acts by Lie derivative everywhere. 
Denote by $b^0 \Omega + b^1 \Omega$ the fields in the decomposition of $\cS^!$ above.

The $L_\infty$ $\cL$-module map $\Phi = \Phi^{(1)} + \Phi^{(2)}$ is defined by
\begin{align*}
\Phi^{(1)} (\gamma^0 + \gamma^1) & = \gamma^0 \Omega + \gamma^1 \Omega \in \Omega^{5,\bu}(X) \oplus \Pi \Omega^{5,\bu}(X, \T^*_X) \\
\Phi^{(2)} (\mu^0 \otimes (\gamma^0 + \gamma^1)) & = \mu^0 \gamma^0 \Omega + \mu^0 \gamma^1 \in \Omega^{5,\bu}(X) \oplus \Pi \Omega^{5,\bu}(X, \T^*) .
\end{align*}
Let us sketch an argument that this is an $L_\infty$ $\cS$-module map.
Suppose $\mu^1 \in \PV^{1,\bu}(X) \Hat{\otimes} \Omega^\bu(M)$.
Then $\mu^1$ acts on $\cM$ by Lie derivative
\[
\mu^1 \cdot (\gamma^0 + \gamma^1) = L_{\mu^1} (\gamma^0) + L_{\mu^1} (\gamma^1) .
\]
So, 
\[
\Phi^{(1)} (\mu^1 \cdot (\gamma^0 + \gamma^1)) - \mu^1 \cdot \Phi^{(1)} (\gamma^0 + \gamma^1) = (\gamma^0 + \gamma^1) L_{\mu^1} \Omega .
\]
The right-hand side is precisely
\[
\Phi^{(2)} ((\partial_\Omega \mu^1) \otimes (\gamma^0 + \gamma^1))
\]
which implies that $\Phi = \Phi^{(1)} + \Phi^{(2)}$ is an $L_\infty$ module map.

%Now, $\Phi$ determines an equivalence of BV theories 
%\[
%\Phi \colon (\cL \ltimes \cL^! [-3]) \xto{\simeq} \cL \ltimes \left(\Omega^{0,\bu}(X) \oplus \Pi \Omega^{1,\bu}(X)\right)
%\]
%where on the left-hand side appears the local Lie algebra underlying BF theory for $\cL$ and the right-hand side appears the local Lie algebra of our modified BF theory, whose action functional we have denoted $\Tilde{S}_{BF}$.

%For BF theory on $\cL$, the fields are described by the local dg Lie algebra
%\[
%\cL \ltimes \Pi \cL^!  
%\]
%whose underlying graded sheaf is $\cL \oplus \Pi \cL^!$ (notice that we have broke the usual $\ZZ$-grading to a $\ZZ/2$-grading). 
%In \eqref{eqn:modified} we have chosen to identify $\cL^!$ with a slightly different $\cL$-module, using the holomorphic volume form. 
%However, the map 
%\[
%\Pi \cL^!  \xto{\Omega^{-1}} \left(\Omega^{0,\bu}(X) \oplus \Pi \Omega^{1,\bu}(X)\right)
%\]
%is {\em not} a map of $\cL$-modules. 
%
%There is, however, an $L_\infty$-map $\Phi$ of $\cL$-modules whose linear part is the map $\Phi^{(1)} = \Omega^{-1}$ above. 
%There is a higher order map of the form
%\[
%\Phi^{(2)} \colon \cL \otimes \Pi \cL^! \to \left(\Omega^{0,\bu}(X) \oplus \Pi \Omega^{1,\bu}(X)\right)
%\]
%defined as follows. 
%
%
%
%Now, consider the functional $J$ which is a local functional on the local Lie algebra describing modified BF theory. 
%One computes the restriction of $J$ along $\Phi$ as
%\[
%(\Phi^* J) (\mu^0 + \mu^1 , b^0 \Omega + b^1 \Omega) = \frac16 \int_{X \times L} b^1 \partial b^1 \partial b^1 + \frac16 \int_{X \times L} \mu^0 b^1 \partial b^1 \partial b^1 .
%\]
%
%
%It is clear that $J$ is closed for the part of the differential arising from the kinetic term $\{S_{\rm free},\cdot\}$.
%It remains to see that\brian{finish}
\end{proof}

\subsubsection{Chern--Simons deformation}
We return back to the theory described by the action functional $S_0$ in \eqref{eqn:modbfaction}. 
We will show that this action admits a deformation which puts it precisely in the form of the action in Definition \ref{dfn:classical}.
We explain how this deformation relates to the familiar Chern--Simons term in eleven-dimensional supergravity in Section \ref{sec:evidence}.

As we defined it, $S_0$ is an action that makes sense on $X \times M$ where $X$ is a Calabi--Yau manifold and $M$ is a smooth manifold, both of arbitrary dimension. 
We are mostly interested in the case that $X$ is a Calabi--Yau five-fold and $M=L$ is a real one-dimensional manifold.
Also, for the deformed action to make sense, we must break the $\ZZ$-grading on the fields described by $S_0$ to a $\ZZ/2$-grading. 
Thus, as a $\ZZ/2$-graded space of fields we have 
\[
  \begin{array}{ccl}
    \mu = \mu^1+\mu^0 & \in & \left(\Pi \pv^{1,\bu}(X) \oplus \pv^{0,\bu}(X) \right) \; \Hat{\otimes} \; \Omega^{\bu}(L) \\
    \gamma = \gamma^0+ \gamma^1 & \in & \left(\Pi \Omega^{0,\bu}(X) \oplus \Omega^{1,\bu}(X) \right) \; \Hat{\otimes}\; \Omega^{\bu}(L) .
  \end{array}
\]
The $\Pi(\cdot)$ denotes the $\ZZ/2$ parity shift.

The action $S_0$ describes the local dg Lie algebra structure on $\cS \ltimes \cM[-3]$ with differential $\dbar + \partial + \d_{dR}$ and brackets
\begin{align*}
[\mu_1, \mu_2] & = \{\mu_1, \mu_2\}_{\rm NS} \\
[\mu^1, \gamma] & = L_{\mu^1} \gamma .
\end{align*}

Consider the following deformation of $S_0$ by the functional 
\[
J = \frac16 \int_{X \times L} (1 + \mu) \gamma \partial \gamma \partial \gamma .
\]
This has the affect of deforming the dg Lie structure to the $L_\infty$ structure described by the same differential and the following $2$-ary $[\cdot, \cdot]$ and $3$-ary operations $[\cdot, \cdot, \cdot]_3$ described by
%\[
%\begin{array}{cccccc}
%[\mu_1, \mu_2] & = & \{\mu_1, \mu_2\}_{\rm NS} \\ 
%[\mu^1, \gamma] & = & L_{\mu^1} \gamma \\
%\]

\[
\begin{array}{rllllll}
[\mu_1, \mu_2] & = & \{\mu_1, \mu_2\}_{\rm NS} \\
{[\mu, \gamma]} & = &  L_{\mu^1} \gamma \\
{[\gamma^1_1, \gamma^1_2]} & = & \Omega \vee \left(\gamma^1_1 \partial \gamma^1_2 \pm \gamma^1_2 \partial \gamma^1_1\right) & \in & \PV^{1,\bu}(X) \,\Hat{\otimes} \, \Omega^\bu(L) . \\
{[\gamma^1_1, \gamma^1_2 , \mu^0]}_3 & = & \mu^0 \Omega \vee \left(\gamma^1_1 \partial \gamma^1_2 \pm \gamma^1_2 \partial \gamma^1_1\right) & \in & \PV^{1,\bu}(X) \, \Hat{\otimes} \, \Omega^\bu(L) \\
{[\gamma^1_1, \gamma^1_2 , \gamma_3^1]}_3 & = & \Omega \vee (\gamma_1^1 \partial \gamma_2^1 \partial \gamma^1_3) & \in & \Omega^{0,\bu}(X) \, \Hat{\otimes} \,\Omega^\bu(L) .

\end{array}
\]
